Review: Crop adaptation through introgression from wild relatives

### 2017-04-07 paper.tex
Update paper.tex

@@

The barley domestication process has reduced the number of alleles in the domesticate to only 40\% of that found in wild barley, though there remains a great deal of phenotypic diversity among the wild barleys \cite{ellis2000wild}\.
Wild-domesticate breeding experiments have shown that wild barleys have alleles for several important agronomic phenotypes, including brittleness, flowering time, plant height, lodging, and yield \cite{von2006ab,handley1994chromosome}\.
The authors of \cite{Poets2015} used STRUCTURE to look for patterns of introgression from wild relatives in a dataset of 803 landraces.
The authors found a high amount variability in the amount of contribution from wild relatives, as well as its location in the genome, within barley populations.
This is indicative of contribution from numerous wild populations.
Furthermore, the authors find that wild introgression contribution is generally greatest from geographically-proximate populations, and that introgressed regions might be combined from geographically-separate wild populations.
Low linkage disequilibrium and small blocks of identity by state indicate that these introgressed regions are old, perhaps dating back to the beginning of domestication.
As landraces and nearby wild relatives share similar genomic sequences, the introgressed regions that are exclusive to that landrace are more more likely to contain adaptive alleles.

>>>>

Whereas the process of domestication used to be concieved of as rapid and geographically-constrained, archaeological and genetic evidence has recently revealed that domestication is more often temporally-protracted and multiregional \cite{brown2009complex}.
This new paradigm emphasizes the role of gene flow of beneficial alleles into domesticating populations from sympatric, locally-adapted wild relatives, a process known as adaptive introgression.
Adaptive introgression has two steps: hybridization between two genomes (in the case of this review, a domesticated crop and its wild relative), followed by recombination and selection for progressively smaller genomic segments that harbor the adaptive locus/loci with fewer maladaptive alleles being dragged along \cite{Feuillet200824}.

@@

The barley domestication process has reduced the number of alleles in the domesticate to only 40\% of that found in wild barley, though there remains a great deal of phenotypic diversity among the wild barleys \cite{ellis2000wild}\.
Wild-domesticate breeding experiments have shown that wild barleys have alleles for several important agronomic phenotypes, including powdery mildew resistance \cite{dreiseitl2017heterogeneity}, brittleness, flowering time, plant height, lodging, and yield \cite{von2006ab,handley1994chromosome}\.
The authors of \cite{Poets2015} used STRUCTURE to look for patterns of introgression from wild relatives in a dataset of 803 landraces.
The authors found a high amount variability in the amount of contribution from wild relatives, as well as its location in the genome, within barley populations.
This is indicative of contribution from numerous wild populations.
Furthermore, the authors find that wild introgression contribution is generally greatest from geographically-proximate populations, and that introgressed regions might be combined from geographically-separate wild populations.
Low linkage disequilibrium and small blocks of identity by state indicate that these introgressed regions are old, perhaps dating back to the beginning of domestication.
As landraces and nearby wild relatives share similar genomic sequences, the introgressed regions that are exclusive to that landrace are more more likely to contain adaptive alleles.
